### 2020-11-16 05_Thesis/THESIS_LaTeX/Chapters/2.tex
chap2 in progress

Near-field electrospinning process parameters and achieved fiber morphology data was collected into a single database with the purpose to analyze the data and find correlations between the process parameters and the obtained fiber morphology after a NFES process. The alalysis comprises from the first reported NFES apparatus built in 2003 by J. Kameoka et al. \cite{Kameoka2003a} to recent studies conducted in 2020. The data collection process was divided in three procedures depending on the format of the available information, as follows:

@@

Scanning Electron Microscopy Images (SEM) images contain information in a two-dimensional grid that can be extracted using point and line counting techniques, however this can be a laborious process for a large number of images. To decrease the complex and lavorious aspect of the counting process, a \emph{Python} script was developed to measure fiber diameters from the available SEM images. As shown in Figure \ref{fig:}, the image analysis algorithm follows three main steps: pre-processing, segmentation, object detection, and data processing.

\section{Discussion \& NFES Challenges}
Helix electrodynamic printing (HE-printing) was presented by Duan et al. \unskip~\cite{527120:11974308} with the intention of depositing aligned fibers. The authors fabricated a stretchable piezoelectric device using micro and nano fibers to demonstrate the possible applications of HE-printinh for electronics manufacturing. Duan et al. concluded that the fiber morphology is mainly driven by: the stage velocity, the applied voltage, and the nozzle-to-collector distance.

\bgroup
%\fixFloatSize{./images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{./images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}{\includegraphics[scale=0.65]{./images/6e169654-19e4-40ab-bb05-8ffb11b5ce11-uplt_cormat.png}}{}
\makeatother 
\caption{{}}
\label{f-30543905e028}
\end{figure*}
\egroup

\bgroup
%\fixFloatSize{./images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{./images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}{\includegraphics{./images/dac8d1ee-e40f-49ab-a2ca-e0d7db210474-uplt_nfesappliedvoltage_vs_fiberdiameter.png}}{}
\makeatother 
\caption{{NFES Applied Voltage vs. Fiber Diameter}}
\label{f-59ed68f95344}
\end{figure*}
\egroup

\bgroup
%\fixFloatSize{./images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{./images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}{\includegraphics{./images/a8f86e3c-c4e3-45be-b9e8-7b60145137cb-uplt_nozzlediameter_vs_fiberdiameter.png}}{}
\makeatother 
\caption{{Nozzle Diameter vs. Fiber Diameter}}
\label{f-51afaccaf109}
\end{figure*}
\egroup

\bgroup
%\fixFloatSize{./images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{./images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}{\includegraphics{./images/6eaa2ba7-07ab-4cfb-980d-5f78b4fcf1a5-uplt_nozzletocollectordistance_vs_fiberdiameter.png}}{}
\makeatother 
\caption{{Nozzle to Collector Distance vs. Fiber Diameter}}
\label{f-5f453fad619f}
\end{figure*}
\egroup

\bgroup
%\fixFloatSize{./images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{./images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}{\includegraphics{./images/b8cbc9c7-97d8-409f-a979-447aebd4aa67-uplt_polymerconcentration_vs_fiberdiameter.png}}{}
\makeatother 
\caption{{Polymer Concentration vs. Fiber Diameter}}
\label{f-d977f56a0782}
\end{figure*}
\egroup

\bgroup
%\fixFloatSize{./images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}
\begin{figure*}[!htbp]
\centering \makeatletter\IfFileExists{./images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}{\includegraphics{./images/085b1fe7-0896-4800-b231-bf68cf86983b-uplt_solutiondepositionrate_vs_fiberdiameter.png}}{}
\makeatother 
\caption{{Solution Deposition Rate vs. Fiber Diameter}}
\label{f-08e527ddef81}
\end{figure*}
\egroup
Electrohydrodynamic (EHD) jet printing is a direct-writing technique which ejects ink through a fine nozzle using an electric field, which has the advantages of high-resolution, rapid printing speed and a wide range of ink selectivity. The effect of parameters such as ink concentration, working distance, applied voltage, and stage speed on the diameter of the printed nano fibers was investigated.

@@

>>>>

Near-field electrospinning process parameters and achieved fiber morphology data was collected into a single database with the purpose to analyze the data and find correlations between the process parameters and the obtained fiber morphology after a NFES process. The alalysis comprises from the first reported NFES apparatus built in 2003 by J. Kameoka et al. \cite{Kameoka2003a} to recent studies conducted in 2020. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014} The data collection process was divided in three procedures depending on the format of the available information, as follows:

@@

Scanning Electron Microscopy Images (SEM) images contain information in a two-dimensional grid that can be extracted using point and line counting techniques, however this can be a laborious process for a large number of images. To decrease the complex and lavorious aspect of the counting process, a \emph{Python} script was developed to measure fiber diameters from the available SEM images. As shown in Figure \ref{fig:imageAnalysisAlgorithm}, the image analysis algorithm follows three main steps: pre-processing, segmentation, object detection, and data processing.

\begin{figure}[!th]
\centering
\includegraphics[scale=0.50]{./Figures/imageAnalysisAlgorithm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{Yousefi2019}}
\label{fig:imageAnalysisAlgorithm}
\end{figure}

The adopted image analysis was implemented with the \emph{Python} package \emph{OpenCV}. First a segmentation procedure is executed over an input image to delimit the objects to be measured (fiber sections and scale bar). The segmentation step is the only step needed to be done manually in a image processing software, in this case \emph{Inkscape} was used. Next, the segmented image is passed to the \emph{Pyhton} script, which will convert its input image into a binary image. A binary image is a black and white image (with no gray scale) that ease the detection of the object edges as the color intensity change between the objects and the background is well defined. Once the binary image is computed, the \emph{Canny} edge detection algorithm is executed. Once the edges are well defined, a the image is dilated to make the edges more visible. The final step before measurement, the \emph{OpenCV} \emph{findContours} function is called to store the objects in memory. The first object to be measured is the scale bar as this is needed as a reference to convert the pixel counts to a metric unit. Finally, the objects are located within the image with four edge points, and the reference object is used to compute the metric length as the ratio of counted pixels between two edge points and the scale bar dimension in meters.

\section{Discussion \& NFES Challenges}

Helix electrodynamic printing (HE-printing) was presented by Duan et al. \unskip~\cite{527120:11974308} with the intention of depositing aligned fibers. The authors fabricated a stretchable piezoelectric device using micro and nano fibers to demonstrate the possible applications of HE-printing for electronics manufacturing. Duan et al. concluded that the fiber morphology is mainly driven by: the stage velocity, the applied voltage, and the nozzle-to-collector distance.

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_corMat.png}
\decoRule
\caption[NFES correlation matrix of process parameters and fiber morphology]{{Correlation matrix comprised by the NFES data from recent literature. 
\cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014} Fiber diameter is highly correlated with polymer solution concentration and slightly correlated with solution flow rate, zero-shear viscosity and nozzle diameter.}}
\label{fig:plt_corMat}
\end{figure}

Figures \ref{fig:plt_Cpolymerwt_vs_Dfiberm}, \ref{fig:plt_Dnozzlem_vs_Dfiberm}, \ref{fig:plt_Lm_vs_Dfiberm}, \ref{fig:plt_Phi0V_vs_Dfiberm}, \ref{fig:plt_Qm3s_vs_Dfiberm} and \ref{fig:plt_vstagems_vs_Dfiberm} are scatter plots that depict the relationship of various process parameters (polymer concentration $C_{polymer}$, nozzle inner diameter $D_{nozzle}$, NFES working distance $L$, NFES applied voltage $\Phi_0$, flow rate $Q$, and stage velocity $v_{stage}$) with the final fiber diameter $D_{fiber}$. In a generalized summary, these figures suggest that thin fibers are produced with the implementation of low polymer concentrations, small nozzle diameters, short working distances, low applied voltages, low flow rates, and high stage xy velocities. Moreover, based on the degree of dispersion of the data points, polymer concentration $C_{polymer}$ is the most reliable process parameter to describe and predict the behavior of the fiber diameter, as most of the data can be grouped in a single cluster. Unlike $C_{polymer}$ in Figure \ref{fig:plt_Cpolymerwt_vs_Dfiberm}, various data clusters can be identified within the other scatter plots. For instance, Song's results \cite{Song2015} deviate from the main cluster in Figures \ref{fig:plt_Dnozzlem_vs_Dfiberm}, \ref{fig:plt_Lm_vs_Dfiberm}, \ref{fig:plt_Phi0V_vs_Dfiberm}, and \ref{fig:plt_vstagems_vs_Dfiberm}, this may be because Song et al. used Au/Pd coated glass capillary nozzles instead of the traditional stainless steel precision tips. However in the $C_{polymer}$ vs. $D_{fiber}$ figure, Song's results fit within the main cluster.

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Cpolymerwt_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Cpolymerwt_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Dnozzlem_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Dnozzlem_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Lm_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Lm_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Phi0V_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Phi0V_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Qm3s_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Qm3s_vs_Dfiberm}
\end{figure}

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_vstagems_vs_Dfiberm.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_vstagems_vs_Dfiberm}
\end{figure}

Electrohydrodynamic (EHD) jet printing is a direct-writing technique which ejects ink through a fine nozzle using an electric field, which has the advantages of high-resolution, rapid printing speed and a wide range of ink selectivity. The effect of parameters such as ink concentration, working distance, applied voltage, and stage speed on the diameter of the printed nano fibers was investigated.

@@

\section{Diameter Prediction of Electrospun Fibers} % adimensional analysis

\begin{figure}[!th]
\centering
\includegraphics[width=\textwidth]{./Figures/plt_Pi1_vs_Oh.png}
\decoRule
\caption[Image Analysis Algorithm to Measure Fiber Diameters from SEM images]{Image Analysis Algorithm to Measure Fiber Diameters from SEM images. Ilustration uses Yousefi et al.'s work as an example. \cite{Helgeson2007,
  Yang2019,Fattahi2017,Shin2019,Wang2015,Parajuli2016,Zheng2010,Fuh2011,Dalton2015,
  Ru2014,Xue2014,Wang2017,Xu2014,Liu2013,Pan2014,Canton2014,Chakraborty2009,Gupta2007,
  He2018,Zhou2011,Chen2013,Williams2018,Choi2017,Pan2019,Lei2015,Lim2019,Park2020,
  Fuh2012,Flores2017,Chang2010,Xu2019,Zhang2019,Shin2018,Fuh2015,Nagle2019,Zheng2012,
  Kameoka2003a,Liu2014,E.King2019,Hochleitner2017,Madou2011,Jiang2018,Husain2016,
  ElectrospinTech2015,Brown2011,Kolan2018,Chang2011,Beachley2011,Camillo2013,Kameoka2003,
  Bu2012,Lee2012,Huang2015,Coppola2020,CisquellaSerra2019,Ruggieri2013,Hochleitner2014,
  Zhu2016,Brown2014,Chang2008,Sonntag2020,Kim2018,Deng2020,Han2019,George2020,Sun2006a,
  Pan2015,Shen2016,Strauss2019,Fuh2013,Sarkar2007,You2017,Wang2018a,Zheng2014,Song2015,
  GaofengZheng2010,Liu2015a,Min2013,Luo2016,Yousefi2019,Cardenas2017,Coppola2014}}
\label{fig:plt_Pi1_vs_Oh}
\end{figure}

### 2020-11-16 05_Thesis/THESIS_LaTeX/main.tex
chapter 1 done?
chapter 2 in progress
chap2 in progress

% Required for inputting international characters
\usepackage[utf8]{inputenc}

@@

@@

\textbf{CEM}   & \textbf{C}ampus \textbf{E}stado de \textbf{M}éxico\\
\textbf{CNWs}  & \textbf{C}arbon \textbf{N}ano-\textbf{w}ire\textbf{s}\\
\textbf{DC}    & \textbf{D}irect \textbf{C}urrent\\
\textbf{EMS}   & \textbf{E}lectro\textbf{m}echanical \textbf{S}pinning\\
\textbf{FFES}  & \textbf{F}ar \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
\textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\
\textbf{MA}    & \textbf{Ma}ssachusetts\\
\textbf{MEMS}  & \textbf{M}icro\textbf{e}lectro\textbf{m}echanical \textbf{S}ystems\\
\textbf{MNT}   & \textbf{M}aestría en \textbf{N}ano\textbf{t}ecnología \emph{(Master of Science in Nanotechnology)}\\
\textbf{MTY}   & \textbf{M}on\textbf{t}erre\textbf{y} \emph{or} Campus \textbf{M}on\textbf{t}erre\textbf{y}\\
\textbf{NFES}  & \textbf{N}ear \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
\textbf{USA}   & \textbf{U}nited \textbf{S}tates of \textbf{A}merica\\
\textbf{UV}    & \textbf{U}ltra\textbf{v}iolet\\

@@

%$a$ & distance & \si{\meter} \\
%$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
Symbol   & Name              & Unit \\
\addlinespace % Gap to separate the Roman symbols from the Greek
$\omega$ & angular frequency & \si{\radian} \\

>>>>

% Required for inputting international characters
\usepackage[utf8]{inputenc}
\DeclareUnicodeCharacter{0301}{} % TODO: remove unicode character in .bib

@@

% table out of margin: any suggestion?
\usepackage{tabularx}
\renewcommand\arraystretch{1.5} % Add extra space between table rows

@@

\textbf{CEM}   & \textbf{C}ampus \textbf{E}stado de \textbf{M}éxico\\
\textbf{CNWs}  & \textbf{C}arbon \textbf{N}ano-\textbf{w}ire\textbf{s}\\
\textbf{DC}    & \textbf{D}irect \textbf{C}urrent\\
\textbf{EMS}   & \textbf{E}lectro\textbf{m}echanical \textbf{S}pinning\\
\textbf{FFES}  & \textbf{F}ar \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
\textbf{ITESM} & \textbf{I}nstituto \textbf{T}ecnonólogico y de \textbf{E}studios \textbf{S}uperiores de \textbf{M}onterrey\\
\textbf{MA}    & \textbf{Ma}ssachusetts\\
\textbf{MEMS}  & \textbf{M}icro\textbf{e}lectro\textbf{m}echanical \textbf{S}ystems\\
\textbf{MNT}   & \textbf{M}aestría en \textbf{N}ano\textbf{t}ecnología \emph{(Master of Science in Nanotechnology)}\\
\textbf{MTY}   & \textbf{M}on\textbf{t}erre\textbf{y} \emph{or} Campus \textbf{M}on\textbf{t}erre\textbf{y}\\
\textbf{NFEMS} & \textbf{N}ear-\textbf{F}ield \textbf{E}lectro\textbf{m}echanical \textbf{S}pinning\\
\textbf{NFES}  & \textbf{N}ear \textbf{F}ield de \textbf{E}lectro\textbf{s}pinning\\
\textbf{USA}   & \textbf{U}nited \textbf{S}tates of \textbf{A}merica\\
\textbf{UV}    & \textbf{U}ltra\textbf{v}iolet\\

@@

%$a$ & distance & \si{\meter} \\
%$P$ & power & \si{\watt} (\si{\joule\per\second}) \\
Symbol   & Name              & Unit \\
\addlinespace % Gap to separate the Roman symbols from the Greek
$\textrm{Mw}$  & Molecular Weight             & $\textrm{g} / \textrm{mole}$ \\
$\eta_0$       & Zero-shear Viscosity         & $\textrm{Pa} \cdot \textrm{s}$	\\
$K$            & Electrical Conductivity      & $\textrm{S} / \textrm{m}$	\\
$\gamma$       & Surface Tension              & $\textrm{N} / \textrm{m}$ \\
$\dot{\gamma}$ & Shear Rate                   & $1 / \textrm{s}$ \\
$\rho$         & Density                      & $\textrm{Kg} / \textrm{m}^3$ \\
$C_{polymer}$  & Polymer concentration        & $\textrm{wt\%}$	\\
$D_{nozzle}$   & Nozzle Inner Diameter        & $\textrm{m}$ \\
$Q$            & Flow Rate                    & $\textrm{m}^3 / \textrm{s}$	\\
$L$            & NFES Working Distance        & $\textrm{m}$	\\
$\Phi_0$       & NFES Applied Voltage         & $\textrm{V}$	\\
$v_{stage}$    & Collector/Stage velocity     & $\textrm{m} / \textrm{s}$ \\
$D_{fiber}$    & Fiber Diameter               & $\textrm{m}$ \\
$FiberGap$     & Distance between fibers      & $\textrm{m}$ \\
$R_{jet}$      & NFES Jet Radius              & $\textrm{m}$ \\
$Oh$           & Ohnesorge number             & NA. \\
$Pe$           & Peclet number                & NA. \\
$Re$           & Reynolds number              & NA. \\
$We$           & Weber number                 & NA. \\
$\Psi$         & Dimensionless Field Strength & NA. \\
